---
title: "Handbag examples"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
  self_contained: no
toc: yes
toc_float: yes
---


This is a test package to play around with R...

Get it started:

```{r}
#devtools::install_github("inductivestep/handbag")
library(handbag)
```



## Enumerating contigency tables

Here are all 2 by 2 tables which where the total sum is 3:

```{r}
enum_contingency_tables(2, 2, 3)
```



## Playing around with spaceships

### Let's go on holiday

```{r include=FALSE}
speed_in_c    <- .8
distance_in_c <- 4

# Calculates the speed in m/s and distance in m
spaceship_speed     <- light_speed(speed_in_c)
distance_from_earth <- light_speed(distance_in_c)

# Work out the contracted length
distance_on_spaceship <- contracted_length(distance_from_earth,
                                           spaceship_speed)
```

You want to travel to a space hotel `r distance_in_c` light years away from earth, so you set off in a spaceship at `r speed_in_c` times the speed of light, *c*.

Length contraction means the distance from the perspective of the spaceship is shorter: `r distance_on_spaceship / light_speed()` light years, which would be experienced as taking `r distance_on_spaceship / spaceship_speed` years at `r speed_in_c`*c*.

From the perspective of earth, the trip would take `r distance_from_earth / spaceship_speed` years, though it would take an additional `r distance_in_c` years for a radio signal to return to say that you arrived okay.



### Let's go on holiday again...

```{r include=FALSE}
speed_in_c    <- 1
```

This time you're going at the speed of light, *c*. Same distance: `r distance_in_c` light years.

```{r include=FALSE}
# Calculates the speed in m/s and distance in m
spaceship_speed     <- light_speed(speed_in_c)
distance_from_earth <- light_speed(distance_in_c)

# Work out the contracted length
distance_on_spaceship <- contracted_length(distance_from_earth,
                                           spaceship_speed)
```

Length contraction means the distance from the perspective of the spaceship is shorter: `r distance_on_spaceship / light_speed()` light years, which would be experienced as taking `r distance_on_spaceship / spaceship_speed` years (no time!) at *c*.

From the perspective of earth, the trip would take `r distance_from_earth / spaceship_speed` years, though it would take an additional `r distance_in_c` years for a radio signal to return to say that you arrived okay.