---
title: "Handbag examples"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    self_contained: no
    toc: yes
    toc_float: yes
    collapsed: false
---

This is a handbag of commands that I find useful.

Get it started:

```{r message=FALSE, warning=FALSE}
devtools::install_github("inductivestep/handbag")
```

```{r}
library(handbag)
```


## Enumerating contigency tables

Here are all 2 by 2 tables in which the total sum is 3:

```{r}
enum_contingency_tables(2, 2, 3)
```

## Analysis helper functions

```{r message=FALSE}
library(tidyverse)
tib <- expand.grid(like_peas   = c(0,1), 
                   like_cheese = c(0,1),
                   like_chips  = c(0,1)) %>% as_tibble()

tib
tib$like <- handbag::binary_patterns_var(tib, "like_")
tib
```


## Special relativity: playing around with spaceships

### Let's go on holiday

```{r include=FALSE}
speed_in_c    <- .8
distance_in_c <- 4

# Calculates the speed in m/s and distance in m
spaceship_speed     <- light_speed(speed_in_c)
distance_from_earth <- light_speed(distance_in_c)

# Work out the contracted length
distance_on_spaceship <- contracted_length(distance_from_earth,
                                           spaceship_speed)
```

You want to travel to a space hotel `r distance_in_c` light years away from earth, so you set off in a spaceship at `r speed_in_c` times the speed of light, *c*.

Length contraction means the distance from the perspective of the spaceship is shorter: `r distance_on_spaceship / light_speed()` light years, which would be experienced as taking `r distance_on_spaceship / spaceship_speed` years at `r speed_in_c`*c*.

From the perspective of earth, the trip would take `r distance_from_earth / spaceship_speed` years, though it would take an additional `r distance_in_c` years for a radio signal to return to say that you arrived okay.


### Let's go on holiday again

```{r include=FALSE}
speed_in_c    <- .999

# Calculates the speed in m/s and distance in m
spaceship_speed     <- light_speed(speed_in_c)
distance_from_earth <- light_speed(distance_in_c)

# Work out the contracted length
distance_on_spaceship <- contracted_length(distance_from_earth,
                                           spaceship_speed)
```

You want to travel to a space hotel `r distance_in_c` light years away from earth, so you set off in a spaceship at `r speed_in_c` times the speed of light, *c*.

Length contraction means the distance from the perspective of the spaceship is shorter: `r distance_on_spaceship / light_speed()` light years, which would be experienced as taking `r distance_on_spaceship / spaceship_speed` years at `r speed_in_c`*c*.

From the perspective of earth, the trip would take `r distance_from_earth / spaceship_speed` years, though it would take an additional `r distance_in_c` years for a radio signal to return to say that you arrived okay.


### Let's go on holiday again - really fast this time...

```{r include=FALSE}
speed_in_c    <- 1
```

This time you're going at the speed of light, *c*. Same distance: `r distance_in_c` light years.

```{r include=FALSE}
# Calculates the speed in m/s and distance in m
spaceship_speed     <- light_speed(speed_in_c)
distance_from_earth <- light_speed(distance_in_c)

# Work out the contracted length
distance_on_spaceship <- contracted_length(distance_from_earth,
                                           spaceship_speed)
```

Length contraction means the distance from the perspective of the spaceship is shorter: `r distance_on_spaceship / light_speed()` light years, which would be experienced as taking `r distance_on_spaceship / spaceship_speed` years (no time!) at *c*.

From the perspective of earth, the trip would take `r distance_from_earth / spaceship_speed` years, though it would take an additional `r distance_in_c` years for a radio signal to return to say that you arrived okay.


### Another example

This one is from [Andrew Duffy](http://physics.bu.edu/~duffy/ns547_spring10_notes03/length_contraction.html). 

```{r include=FALSE}
speed_in_c    <- .95
distance_in_c <- 9.5

# Calculates the speed in m/s and distance in m
spaceship_speed     <- light_speed(speed_in_c)
distance_from_earth <- light_speed(distance_in_c)

# Work out the contracted length
distance_on_spaceship <- contracted_length(distance_from_earth,
                                           spaceship_speed)
```

You want to travel to a space hotel `r distance_in_c` light years away from earth, so you set off in a spaceship at `r speed_in_c` times the speed of light, *c*.

Length contraction means the distance from the perspective of the spaceship is shorter: `r distance_on_spaceship / light_speed()` light years, which would be experienced as taking `r distance_on_spaceship / spaceship_speed` years at `r speed_in_c`*c*.

From the perspective of earth, the trip would take `r distance_from_earth / spaceship_speed` years, though it would take an additional `r distance_in_c` years for a radio signal to return to say that you arrived okay.